\begin{thebibliography}{99} % Bibliography

\bibitem[1] {1}
S. Cecchini, M. Spurio, Atmospheric muons: experimental aspects,
{\em arXiv}:1208.1171v1 [astro-ph.EP].

\bibitem[2] {2}
J.Crookes, B.Rastin, An investigation of the absolute intensity of muons at sea-level, 
{\em Nucl. Phys. B} 39 (1972) 493.

\bibitem[3] {3}
K.Greisen, The intensities of the hard and soft components of cosmic rays as functions of altitude and
zenith angle,
{\em Phys. Rev.} 61 (1942) 212.

\bibitem[4] {4}
B. Rossi, Interpretation of cosmic-ray phenomena,
{\em Rev. Mod. Phys.} 20 (1948) 537.

\bibitem[5] {5}
R.J.R.Judge, W.F.Nash, Measurements on the Muon Flux at Various Zenith Angles,
{\em Nuovo Cimento} 35 (1965) 999.

\bibitem[6] {6}
S.Fukui, T.Kitamura, Y.Murata, On the range spectrum of $\mu$-mesons at sea-level at geomagnetic latitude $\SI{24}{\degree N}$,
{\em J. Phys. Soc. Jpn.} 12 (1957) 854.

\bibitem[7] {7}
Peter K.F. Greider, Cosmic rays at Earth: researchers reference manual and data book.

\bibitem[8] {8}
N.Karmakar, A.Paul, N.Chaudhuri, Measurements of absolute intensities of cosmic-ray muons
in the vertical and greatly inclined directions at geomagnetic latitudes $\SI{16}{\degree N}$, 
{\em Nuovo Cim. B} 17 (1973) 173.

\bibitem[9] {9}
M.S. Sinha, N. Basu,
{\em Indian J. Phys.} 33 (1959) 335.

\bibitem[10] {10}
S.Pal, B.Acharya, G.Majumder, N.Mondal, D.Samuel, B.Satyanarayana, Measurement of integrated flux of cosmic ray muons at sea level using the INO-ICAL prototype detector,
{\em J. Cosmol. Astropart. Phys.} 07 (2012) 033.

\bibitem[11] {11}
O.C.Allkofer, R.D.Andresen, W.D.Dau, The muon spectra near the geomagnetic equator,
{\em Can. J. Phys.} 46 (1968) S301.

\bibitem[12] {12}
S. Pethuraja,b, V.M. Datarb, G. Majumderb, N.K. Mondalc, K.C. Ravindranb and B. Satyanarayanab, 
Measurement of cosmic muon angular distribution and vertical integrated flux by $\SI{2}{m} \times \SI{2}{m}$ RPC stack at IICHEP-Madurai, 
{\em J. Cosmol. Astropart. Phys.} 09 (2017) 021. 

\end{thebibliography}
